---
title: "Final Report - Bram Koudijs"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bg: white
      fg: black 
      primary: "#E5A945"
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(dplyr)
library(spotifyr)
library(compmus)
library(tidyverse)

```

Hip-hop or pop {.storyboard}
=====================================

### Tempo, Duration and Volume 

```{r}
DrakeTop <-
  get_playlist_audio_features(
    "",
    "7dl2AkcjDVWdVxwCH2QAWV"
  ) |>
  slice(1:25) |>
  add_audio_analysis()
RapCaviar <-
  get_playlist_audio_features(
    "",
    "37i9dQZF1DX0XUsuxWHRQd"
  ) |>
  slice(1:25) |>
  add_audio_analysis()
Popchart <-
  get_playlist_audio_features(
    "",
    "1eKpGEx2H4cB6DBs34obeR"
  ) |>
  slice(1:25) |>
  add_audio_analysis()

DrakeCaviar <-
  DrakeTop |>
  mutate(Category = "Drake Top Songs") |>
  bind_rows(RapCaviar |> mutate(Category = "Hip hop Charts"), Popchart |> mutate(Category = "Pop Charts"))


Drakegg <- DrakeCaviar |>
  mutate(
    sections =
      map(
        sections,                                    # sections or segments
        summarise_at,
        vars(tempo, loudness, duration),             # features of interest
        list(section_mean = mean, section_sd = sd)   # aggregation functions
      )
  ) |>
  unnest(sections) |>
  ggplot(
    aes(
      x = tempo,
      y = tempo_section_sd,
      colour = Category,
      alpha = loudness
    )
  ) +
  geom_point(aes(size = duration / 60)) +
  geom_rug() +
  theme_minimal() +
  ylim(0, 5) +
  labs(
    x = "Mean Tempo (bpm)",
    y = "SD Tempo",
    colour = "Category",
    size = "Duration (min)",
    alpha = "Volume (dBFS)"
  )


```

***
In this graph we compare tempo, loudness and duration in sections. Because it takes a lot of time to load the data from the corpus for this comparison, i only used 25 songs per category. I compared the top 25 songs of drake, with 25 songs from the Hip-hop charts, and 25 songs from the pop charts. It stands out that a lot of drake songs have low Mean Tempo. Might that be a trademark for drake? Another interesting finding is that some songs in the Hip-Hop chart score pretty high on the SD Tempo. Where a lot of the top drake songs score more like the songs in the pop chart. 

This might be a little fast to conclude due to the little sample size. For my final portfolio i would like to plot this graph with some more data. 


Keys and Chords {.storyboard}
=====================================


### Drake - Passionfruit chords 
```{r}


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

PassionChords <-
  get_tidy_audio_analysis("5mCPDVBb16L4XQwDdbRUpz") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )

PassionChords |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***
In this section we are comparing the keys and chords of two songs. The first song "Passionfruit" is seen before. This is the best scoring song of Drake. The other song is "Rockstar by Postmalone", the number one in the Billboard Hip-Hop top 100. Right here we see the chordogram of "Passionfruit" as we can see, that Gb7 is the most obvious followed by Ab7, Eb7 and A7. In the next page we will compare this to the chordogram of "Rockstar". For both graphs the best visualization was found with the Euclidean distance metric and the Manhattan norm. 

### Hip-Hop - Rockstar chords

```{r}


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

RockstarChords <-
  get_tidy_audio_analysis("0e7ipj03S05BNilyu5bRzt") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )

RockstarChords |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***
This graph is more clear in my opinion. In the beginning of the song (about the first 10 seconds) we see a lot of yellow colors in the graph. This is due to the bass-less intro where there only is a flute playing. When the rest of the instruments kick in, we see the A7 and Eb7 as the most prominent chords. When we compare this to the chordogram of "Passionfruit" we see that A7 and Eb7 also are found, just not as the most prominent chords. 

We may say that the A7 and Eb7 chords are most likely used a lot in Hip-hop music. To go into the question of this portfolio, we will also compare the chordrogram of Passionfruit with one of the best scoring pop songs of today. 

### Pop - Flowers chords

```{r}


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

FlowersChords <-
  get_tidy_audio_analysis("0yLdNVWF3Srea0uzk55zFn") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )

FlowersChords |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

***

In this graph we can see that the song 'Flowers' has ocurences of the chords D7, A7, E7. We can also see some color change at G7 and C7. This differs quite a bit from "Passionfruit" and "Rockstar". The only overlapping chord we can find is A7. Another interesting feature of this song is that all the cords are seventh chords. This means that it are all triads with an added note forming an interval of a seventh above the cords root. 

Cepstrograms {.storyboard}
=====================================

### Passionfruit

```{r}


passion <-
  get_tidy_audio_analysis("5mCPDVBb16L4XQwDdbRUpz") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

passion |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() + ggtitle("Passionfruit Cepstrogram") +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()



```

***
Just adding some text to see what it looks like in the storyboard

### Started from the bottom 
```{r}


Started <-
  get_tidy_audio_analysis("3dgQqOiQ9fCKVhNOedd2lf") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

Started|>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() + ggtitle("Started from the bottom Cepstrogram") +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()



```

Chromagrams {.storyboard}
=====================================

### Passionfruit
```{r}
Passionfruit <-
  get_tidy_audio_analysis("5mCPDVBb16L4XQwDdbRUpz") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

Passionfruit |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() + ggtitle("Passionfruit - chromagram") +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```

### Started from the bottom
```{r}
Started1 <-
  get_tidy_audio_analysis("3dgQqOiQ9fCKVhNOedd2lf") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

Started1 |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() + ggtitle("Started from the bottom - chromagram") +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```

### Explanation

Corpus comparison {.storyboard}
=====================================


### Mode, Valence and Energy

```{r}

Topsongsdrake <- get_playlist_audio_features("", "7dl2AkcjDVWdVxwCH2QAWV")
HipHopchart <- get_playlist_audio_features("", "6pJuFS2IWvgIJkdxrM9ncV")

hiphopdrake <-
  bind_rows(
    Topsongsdrake |> mutate(category = "TopSongs"),
    HipHopchart |> mutate(category = "HipHop")
  )
                                
hiphopdrake |>                    # Start with awards.
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  
  ggplot(                     # Set up the plot.
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  geom_text(                  # Add text labels from above.
    aes(
      x = valence,
      y = energy,
      label = label
    ),
    data = 
      tibble(
        label = c("Altijd wel iemand", "ENERGY"),
        category = c("TopSongs", "HipHop"),
        valence = c(0.090, 0.123),
        energy = c(0.101, 0.967)
      ),
    colour = "black",         # Override colour (not mode here).
    size = 3,                 # Override size (not loudness here).
    hjust = "left",           # Align left side of label with the point.
    vjust = "bottom",         # Align bottom of label with the point.
    nudge_x = -0.05,          # Nudge the label slightly left.
    nudge_y = 0.02            # Nudge the label slightly up.
  ) +
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL       # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Paired"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.
    guide = "none"            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )
```



### Started from the bottom 
```{r}


Started <-
  get_tidy_audio_analysis("3dgQqOiQ9fCKVhNOedd2lf") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

Started|>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() + ggtitle("Started from the bottom Cepstrogram") +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()



```